# Roles and Responsibilities {#roles}

As of Spring Semester 2020, the organizational structure of Eagle I.O is:

```{r trying, echo=FALSE, warning=FALSE, message=FALSE}

library(grid)
library(Gmisc)

grid.newpage()
# set some parameters to use repeatedly
facx <- .2
midx <- .5
leftx <- .1
leftm <- .35
rightm <- .65
rightx <- .9

gp <- gpar(fill = "cornflowerblue")
# create boxes
(total <- boxGrob("Faculty\n Advisor", 
 x=facx, y=.6, box_gp = gp, height=.15))

(rando <- boxGrob("Governance\n Officer", 
 x=midx, y=.6, box_gp = gp, height=.15))
# connect boxes like this
connectGrob(total, rando, "h")

(g1 <- boxGrob("Marketing\n Officer", 
 x=leftx, y=.3, box_gp = gp, height=.15))    ## using "height" to help with forced breaks

(g2 <- boxGrob("Mentorship\n Coordinator", 
 x=leftm, y=.3, box_gp = gp, height=.15))



(g3 <- boxGrob("Engagement\n Officer", 
 x=rightm, y=.3, box_gp = gp, height=.15))

(g4 <- boxGrob("Parlimentarian", 
 x=rightx, y=.3, box_gp = gp, height=.15))

connectGrob(rando, g1, "N")
connectGrob(rando, g2, "N")
connectGrob(rando, g3, "N")
connectGrob(rando, g4, "N")

```

```{r OrgChart, echo=FALSE, warning=FALSE}

## library(DiagrammeR)

## DiagrammeR("graph TB;
##    A(Rounded)-->B[Squared];
##    B---C{Rhombus!};
##    C-->D>flag shape];
##    C-->E((Circle));")


```


Additional roles can be assigned on an as neded (e.g., project-by-project) basis. The primary responsibilities of these position holders is presented below. Note that elected officers and program managers always function as team leads - they are ultimately responsible for the listed information, but they are expected to execute tasks within teams:


```{r roles, echo=FALSE, warning=FALSE, message=FALSE}

fac <- c("Long-term visioning (5-year plan)","Annual goal-setting and monitoring (projects, clients, research)","Budgeting and staffing", "")

govern <- c("Meet with advisor to create bi-weekly agenda ","Ensure group dynamic is working ","Lead bi-weekly meetings","GroupMe coordinator")

market <- c("Create and keep web page updated","Maintain alumni relations and contact information ","Maintain and update flyer for promotion of group","Coordinate logistics of annual events (orientation, mid-year soiree, SIOP, etc.)")

engage <- c("Administration, scoring, and reporting","Norms development and maintenance","Ongoing validation studies and technical report generation","Delegating project-related tasks to others")

mentor <- c("Keep track of mentor-mentee communications","Ensure all incoming first year students have a mentor (pairing process)","Update calendar of activities and communicate with program participants","Keep track of mentors and mentees - Holding them accountable for meetings and communication")

parl <- c("Seek out and follow-up on project leads","Check Eagle IO email and communicate","Take notes during meetings and uploading to share drive","Keep track of the agenda during meetings")

together <- as.data.frame(cbind(fac, govern,market,engage,mentor,parl))

library(kableExtra)

kable(together, col.names = c("Faculty\nAdvisor",
                           "Governance\nOfficer",
                           "Marketing\nOfficer",
                           "Engagement\nCoordinator",
                           "Mentorship\nCoordinator",
                           "Parlimentarian"))

```

This is a placeholder chart intended to estimate the amount of reliance of each role upon each other. Directionality is also indicated, but all of these numbers are mere esitmates.

```{r FunkyInteractiveChart, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=11}
## library(DiagrammeR)
## DiagrammeR("graph TB;
##    A(Rounded)-->B[Squared];
##    B---C{Rhombus!};
##    C-->D>flag shape];
##    C-->E((Circle));")
### Trying with Eagle I.O
m <- matrix(c(0, 10, 8, 1, 10, 1,
              10, 0, 5, 5, 2,  3,     
              3,  3, 0, 3, 7,  5,  
              3,  5, 6, 0, 0,  6,     
              10, 5, 5, 0, 0,  1,   
              7, 10, 3, 1, 1,  0),              
            byrow = TRUE,
            nrow = 6, ncol = 6)
contact <- c("Faculty", "Governance", "Marketing", "Mentorship", "Engagement", "Parliment")
dimnames(m) <- list(plans = contact,
                    executes = contact)
library(chorddiag)
groupColors <- c("#000000", "#FFDD89", "#957244", "#FF0000", "#8B0000", "#FF8C00")
chorddiag(m, groupColors = groupColors, showTicks = F, groupnamePadding = 20, groupnameFontsize = 12)
```

## Role conflict

> There would need to be a section to deal with "conflict between individuals" because it's only a matter of time
