# Governance {#governance}

```{r kitty3, echo=FALSE, warning=FALSE}
htmltools::tags$iframe(title = "Embedded HTML", src = "./gifs/giphy.gif", height=490, width=490)
```

## Meetings - testing

All members are expected to participate for a minimum of 1.5 years (one Fall semester, two Spring semesters, and to be reasonably available over Winter and Summer breaks). 

* Time requirements of Eagle I.O members 
    + Meetings are mandatory - there is one excused absence per academic semester (Fall and Spring)
        + If you miss *more than one* meeting, and cannot call or make other arrangements for your virtual attendence, you will be put on probation (1 semester term) 
        + If you miss another meeting while on probation you will be expelled from Eagle I.O and fed to **Sir pSyCaDeLiCaT** in an agonizingly painful yet exceedingly beautiful ceremony
    + Keep track of the inbox *if you are the Parlimentarian*

## Consultant Development Plan 

* Either have each consultant discuss and fill out their own individual development plan in terms of Eagle I.O or have a development plan (filled out together) for the organization
    + Potential skills: professional, technical, or R-related skills
    + Meet with Kulas in *April of 1st year* to determine personal consultant goal that will be accomplished prior to graduation (in roughly 1 year)

> The development plan - maybe you could provide some insights on these.

## Structure

As of Spring Semester 2020, the formal roles of Eagle I.O are:

+ Faculty roles
        + Advisor (primary)
        + Advisor (mentorship)

+ Student roles
        + Governance officer
        + Mentorship officer
        + Engagement officer
        + Marketing officer
        + Web officer
        + Parlimentarian 
        + R guru

The following chart is intended to estimate the amount of reliance of each role upon each other. Directionality is also indicated, but all of these numbers are mere esitmates.

```{r FunkyInteractiveChart, include=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=11}

## Add three roles: Faculty Mentorship Advisor, Web Officer, R Guru

## library(DiagrammeR)
## DiagrammeR("graph TB;
##    A(Rounded)-->B[Squared];
##    B---C{Rhombus!};
##    C-->D>flag shape];
##    C-->E((Circle));")
### Trying with Eagle I.O
m <- matrix(c(0, 10, 8, 1, 10, 1, 1, 5, 5,
              10, 0, 5, 5, 2,  3, 2, 4, 4,    
              3,  3, 0, 3, 7,  5, 3, 3, 3,
              3,  5, 6, 0, 0,  6, 4, 2, 2,    
              10, 5, 5, 0, 0,  1, 5, 1, 1, 
              7, 10, 3, 1, 1,  0, 6, 1, 1,
              1,  2, 3, 4, 5,  6, 7, 1, 1,
              1,  2, 3, 4, 5,  6, 7, 8, 9,
              1,  2, 3, 4, 5,  6, 7, 8, 9),              
            byrow = TRUE,
            nrow = 9, ncol = 9)

contact <- c("Faculty", "Governance", "Marketing", "Mentorship", "Engagement", "Parliment", "R", "Web", "Faculty2")

dimnames(m) <- list(plans = contact,
                    executes = contact)

library(chorddiag)

groupColors <- c("#000000", "#FFDD89", "#957244", "#FF0000", "#8B0000", "#FF8C00", "#FF0000")

chorddiag(m, showTicks = F, groupnamePadding = 20, groupnameFontsize = 12)

## groupColors = groupColors, 

```

```{r trying, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}

library(grid)
library(Gmisc)

## add Web 

grid.newpage()
# set some parameters to use repeatedly
facx <- .2
midx <- .5
leftx <- .1
leftm <- .35
rightm <- .65
rightx <- .9

gp <- gpar(fill = "cornflowerblue")
# create boxes
(total <- boxGrob("Faculty\n Advisor", 
 x=facx, y=.6, box_gp = gp, height=.15))

(rando <- boxGrob("Governance\n Officer", 
 x=midx, y=.6, box_gp = gp, height=.15))
# connect boxes like this
connectGrob(total, rando, "h")

(g1 <- boxGrob("Marketing\n Officer", 
 x=leftx, y=.3, box_gp = gp, height=.15))    ## using "height" to help with forced breaks

(g2 <- boxGrob("Mentorship\n Coordinator", 
 x=leftm, y=.3, box_gp = gp, height=.15))



(g3 <- boxGrob("Engagement\n Officer", 
 x=rightm, y=.3, box_gp = gp, height=.15))

(g4 <- boxGrob("Parlimentarian", 
 x=rightx, y=.3, box_gp = gp, height=.15))

connectGrob(rando, g1, "N")
connectGrob(rando, g2, "N")
connectGrob(rando, g3, "N")
connectGrob(rando, g4, "N")

```

Additional roles can be assigned on an as neded (e.g., project-by-project) basis. The primary responsibilities of these position holders is presented below. Note that elected officers and program managers always function as team leads - they are ultimately responsible for the listed information, but they are expected to execute tasks within teams:


```{r roles, echo=FALSE, warning=FALSE, message=FALSE}

fac <- c("Long-term visioning (5-year plan)","Annual goal-setting and monitoring (projects, clients, research)","Budgeting and staffing", "")

govern <- c("Meet with advisor to create bi-weekly agenda ","Ensure group dynamic is working ","Lead bi-weekly meetings","GroupMe coordinator")

market <- c("Create and keep web page updated","Maintain alumni relations and contact information ","Maintain and update flyer for promotion of group","Coordinate logistics of annual events (orientation, mid-year soiree, SIOP, etc.)")

engage <- c("Administration, scoring, and reporting","Norms development and maintenance","Ongoing validation studies and technical report generation","Delegating project-related tasks to others")

mentor <- c("Keep track of mentor-mentee communications","Ensure all incoming first year students have a mentor (pairing process)","Update calendar of activities and communicate with program participants","Keep track of mentors and mentees - Holding them accountable for meetings and communication")

parl <- c("Seek out and follow-up on project leads","Check Eagle IO email and communicate","Take notes during meetings and uploading to share drive","Keep track of the agenda during meetings")

together <- as.data.frame(cbind(fac, govern,market,engage,mentor,parl))

library(kableExtra)

kable(together, col.names = c("Faculty\nAdvisor",
                           "Governance\nOfficer",
                           "Marketing\nOfficer",
                           "Engagement\nCoordinator",
                           "Mentorship\nCoordinator",
                           "Parlimentarian"))

```


## Role conflict

> There would need to be a section to deal with "conflict between individuals" because it's only a matter of time
